Historical Supply of Residual Biomass from Timber Harvest in West-central Alberta, Canada

### 2021-10-08 analysis/manuscript.Rmd
new residue values and some fresh text

## 30 m harvest raster

  * for 1985 - 2015
  * Canada wide and 30 m resolution
  * description
  * clipped to Alberta boundary from GENESIS

@@

  * from GENESIS

## 3 mill locations

* Edson (OSB plant)
* Hinton (pulp mill)
* Whitecourt (Millar Western pulp mill)

## 3 alternative capacities

* 200,000 odmt/yr (small pellet mill)
* 400,000 odmt/yr (large pellet mill, small ethanol plant)
* 800,000 odmt/yr (large ethanol plant)

## Harvest area by township by year

>>>>

## Harvested area

Canada's National Forest Inventory System (NFIS) is a product of the Canadian
Council of Forest Ministers (CCFM).  One of the data sets provided by the NFIS
identifies locations of forest harvesting across Canada for the years 1985-2015
detected from Landsat satellite imagery.  These data are at a 30 m spatial 
resolution.  The data were downloaded from
https://opendata.nfis.org/downloads/forest_change/CA_forest_harvest_mask_year_1985_2015.zip
(accessed 2020-03-05).
The data set is described in @Hermosilla2016.

The data were clipped to the Alberta provincial boundary which was obtained from
Altalis (https://www.altalis.com, accessed 2021-09-10), which manages much of the spatial information
belonging to the Alberta government.

@@

For our analysis, most of our information was aggregated to the township level.
In Alberta, the legal description of any parcel of land uses the Alberta Township
Survey System (see https://www.alberta.ca/alberta-township-survey-system.aspx, 
accessed 2021-10-08). Most townships are roughly square in shape, with an average 
area of about 9,533 ha.  The GIS coverage for township outlines was obtained 
from Altalis (https://www.altalis.com, accessed 2021-09-10).

The harvest areas obtained from the NFIS forest harvesting data set were
aggregated to the township level so that the harvest area for each township
in each of the years from 1985-2015 was recorded in a data set.

## Hypothetical plant locations and capacities

For this study, we assumed that forest harvest residue processing would take place
at a plant co-located with an existing forest products manufacturing facility.
We used the Weyerhaeuser oriented strand board plant in Edson, the Millar Western
Forest Products Ltd. pulp mill in Whitecourt, and the West Fraser pulp mill 
in Hinton as the locations
for the hypothetical forest residue processing facilities.

As well as considering locations for the hypothetical plants, we considered
3 different pland capacities: 200,000 odmt/yr corresponding to a small 
wood pellet mill, 400,000 odmt/yr corresponding to a large pellet mill or
a small ethanol plant, and 800,000 odmt/yr corresponding to a large ethanol 
plant.
